Dependently Typed Multi-stage Calculus

### 2019-11-22 slides/main.tex
Add section pages.
Fixing.

% Output the outline slide
% \begin{frame}{Contents}
%   \tableofcontents
%   \note{
%   }
% \end{frame}

@@

\begin{frame}[fragile]{Our Approach: \LMD}
    Introduce dependent types into \LTP [Hanada\&Igarashi'14].
    \begin{itemize}
        \item Features of multi-stage programming
            \begin{itemize}
                \item Code type
                \item Type safe {\bf{run}}
                \item Cross Stage Persistence(CSP)
            \end{itemize}
        \item Features of dependent types
            \begin{itemize}
                \item Typing, Kinding, Well-formed kind rules with stages
                \item Equivalence rules including CSP
            \end{itemize}
    \end{itemize}
    \note{
        Our approach to the problem of multi-stage programming is introducing dependent types into a multi-stage calculus by Hanada and Igarashi.
        We call our multi-stage calculus as \LMD.
    }
\end{frame}

@@

\begin{frame}[fragile]{Example of \LTP}
    \begin{table}
        \begin{tabular}{ c | c | c }
            & \LTP & MetaOCaml \\[2mm]
            \hline
            Make code & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = .<(1+2)>.| \\[2mm]
            Embed code & \( (\TB (\TBL a + \TBL a)) \) & \verb| .<(.~a)+(.~a)>.| \\[2mm]
            Run code & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run .<(1+2)>.| \\[2mm]
            Code type & \( \TW\ \text{Int} \) & \verb| int code |
        \end{tabular}
    \end{table}
\end{frame}

@@

@@

\begin{frame}[fragile]{Problem of vadd3}
    Hard to compose with other functions.
    \newcommand{\Vn}{\text{Vec}\ \%n}
    \newcommand{\Vpt}{\text{Vec}\ \%3}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \begin{tabbing}
        \hspace{5mm} \= \( \text{val}\ \text{vadd3} : \TW (\Vpt \to \Vpt \to \Vpt) \) \\
        \> \( \text{val}\ \text{double} : \TW (\Vt \to \Vt) \) \\[2mm]
        \> \( \textbf{let}\ \text{add-double}\ v\ w = \) \\
        \> \hspace{5mm} \( \TB (\TBL\text{double}\ (\TBL \text{vadd3}\ \TBL v\ \TBL w));; \) \\
    \end{tabbing}
\end{frame}

\begin{frame}[fragile]{Solution}
    \newcommand{\Vt}{\text{Vec}\ 3}
    Introduce \QPercent.
    \begin{center}
        \infrule[{\QPercent}]{
            M \text{ is a closed term.}
        }{
            \G\vdash \%_\alpha M \E M : \tau
        }
    \end{center}
    Erase the symbol of \( \% \) under the condition.
    \begin{itemize}
        \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \)
    \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Conclusion \& Future Works}
    \begin{block}{Conclusion}
        We introduced dependent types into muti-stage programming.
        \begin{itemize}
            \item Define typing, kinding, well-formed kinding rules including stages.
            \item Define equality rules.
            \item Prove type soundness.
        \end{itemize}
    \end{block}
    \begin{block}{Future Works}
        \begin{itemize}
            \item Algorithmic Typing
        \end{itemize}
    \end{block}
    \note{
    }
\end{frame}

>>>>

% Output the outline slide
% \begin{frame}{Contents}
%     \tableofcontents[currentsection]
%   \note{
%   }
% \end{frame}

@@

\begin{frame}[fragile]{Our Approach: \LMD}
    Introduce dependent types into \LTP [Hanada\&Igarashi'14].
    \begin{itemize}
        \item Features of multi-stage programming
        \item Features of dependent types
    \end{itemize}
    Our contribution
    \begin{itemize}
        \item Define typing, kinding, well-formed kind rules with stages
        \item Define equivalence rules including CSP
    \end{itemize}
    \note{
        Our approach to the problem of multi-stage programming is introducing dependent types into a multi-stage calculus by Hanada and Igarashi.
        We call our multi-stage calculus as \LMD.
    }
\end{frame}

\section{Existing Multi-stage Calculus \LTP}

\begin{frame}{Contents}
    \tableofcontents[currentsection]
    \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Example of \LTP}
    \begin{table}
        \begin{tabular}{ c | c | c }
            & \LTP & MetaOCaml \\[2mm]
            \hline
            Quote & \( \textbf{let } a = \TB (1 + 2) \) & \verb| let a = .<(1+2)>.| \\[2mm]
            Unquote & \( (\TB (\TBL a + \TBL a)) \) & \verb| .<(.~a)+(.~a)>.| \\[2mm]
            Run & \( \textbf{run } (\TB (1 + 2)) \) & \verb| run .<(1+2)>.| \\[2mm]
            Code type & \( \TW\ \text{Int} \) & \verb| int code |
        \end{tabular}
    \end{table}
\end{frame}

@@

\section{Extend \LTP with Dependent Types}

\begin{frame}{Contents}
    \tableofcontents[currentsection]
  \note{
  }
\end{frame}

@@

\begin{frame}[fragile]{Problem of type of vadd3}
    Hard to combine with other functions.
    \newcommand{\Vn}{\text{Vec}\ \%n}
    \newcommand{\Vpt}{\text{Vec}\ \%3}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \begin{tabbing}
        \hspace{5mm} \= \( \text{val}\ \text{vadd3} : \TW (\Vpt \to \Vpt \to \Vpt) \) \\
        \> \( \text{val}\ \text{double} : \TW (\Vt \to \Vt) \) \\[2mm]
        \> \( \textbf{let}\ \text{add-double}\ v\ w = \) \\
        \> \hspace{5mm} \( \TB (\TBL\text{double}\ (\TBL \text{vadd3}\ \TBL v\ \TBL w));; \) \\
    \end{tabbing}
\end{frame}

\begin{frame}[fragile]{Solution}
    \newcommand{\Vt}{\text{Vec}\ 3}
    \newcommand{\Vpt}{\text{Vec}\ \%3}
    Introduce \QPercent.
    \begin{center}
        \infrule[{\QPercent}]{
            M \text{ is a closed term.}
        }{
            \G\vdash \%_\alpha M \E M
        }
    \end{center}
    Erase the symbol of \( \% \) under the condition.
    \begin{itemize}
        \item \( \text{Vec}\ \%3 \E \text{Vec}\ 3 \)
        \item \( \text{vadd3} : \TW (\Vt \to \Vt \to \Vt) \) \\
            \hspace{15mm} \( (\E  \TW (\Vpt \to \Vpt \to \Vpt)) \)
    \end{itemize}
\end{frame}

\begin{frame}[fragile]{Conclusion}
        We introduced dependent types into muti-stage programming.
        \begin{itemize}
            \item Define typing, kinding, well-formed kinding rules for multi-stage calculus.
            \item Define equality rules.
                \begin{itemize}
                        \item Especially, dealing with CSP.
                \end{itemize}
            \item Prove type soundness.
        \end{itemize}
    \note{
    }
\end{frame}

@@
